When are Fuzzy Extractors Possible?

### 2014-10-07 info-bounds/FuzzyExtPossibility.tex
changing notation for maximum number of points in a ball

Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t,W,max} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.   For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log |B_{t,W,max}|.\label{eq:fuzz for flat}
\end{align}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |B_{t,W,max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t,W,max}| + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t,W,max}| - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t,i,W, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t,W_i,max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).  In the binary Hamming space a large fraction of any set of bounded size is the near ``boundary'' of that set.  This will be important for our proof.  We will embed the larger alphabet we used into the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t,W,max}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t,W,max}|-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t,W,max}|-1$.  This completes the proof.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t,W_i,max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t,W_i,max}|-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t,W_i,max}|$.

@@

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,W_i, max}|$ as there at $|B_{t,W_i,max}|$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t,W_i,max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t,W_i,max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot |B_{t,W_i,max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t,W_i,max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

@@

\lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
\bnote{fine with it being here as the FE case lives in the appendix too}
\begin{lemma}
\label{lem:log-minus-one}
For any real numbers $\alpha \leq \beta$ with $\beta \ge e+1$ (in particular, $\beta\ge 4$ suffices), the following holds:
$\alpha \log (\beta-1) > (\alpha-1)\log \beta$. 
\end{lemma}

\begin{proof}
Because $\beta-1$ is positive, and $1+x<e^x$ for positive $x$,
$$1+\frac{1}{\beta-1} < e^{\frac{1}{\beta -1}}\,.$$  Therefore, 
$$\left(1+\frac{1}{\beta-1}\right)^{\alpha-1} < e^{\frac{\alpha-1}{\beta-1}}\le e < \beta-1$$ (since $\alpha\le \beta$). Multiplying both sides by $(\beta-1)^{\alpha-1}$, we obtain
$$\beta^{\alpha-1} < (\beta-1)^\alpha\,.$$
Taking the logarithm of both sides yields the statement of the lemma.
\end{proof}

@@

%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.  We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
\begin{definition}
A set $S$ is a $\beta$-deficient ball if there exists a point $x$ such that $B_{\beta-1}(x) \subseteq S \subseteq B_{\beta}(x)$.
\end{definition}

@@

\begin{lemma}
$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
\end{lemma}
\begin{proof}
By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\beta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).  Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\beta+t$).
We now find bound the size of $S_{p^*, \key^*}$.

>>>>

Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.   For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
\end{align}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).  A  property of the binary Hamming space is that a large fraction of any set of bounded size is the near ``boundary'' of that set.  This will be crucial in our proof.  We will embed the larger alphabet we used into the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.  This completes the proof.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t,i}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.

@@

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*\beta_{t,i}/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

@@

\lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
\bnote{fine with it being here as the FE case lives in the appendix too}
\begin{lemma}
\label{lem:log-minus-one}
For any real numbers $\alpha \leq \eta$ with $\eta \ge e+1$ (in particular, $\eta\ge 4$ suffices), the following holds:
$\alpha \log (\eta-1) > (\alpha-1)\log \eta$. 
\end{lemma}

\begin{proof}
Because $\eta-1$ is positive, and $1+x<e^x$ for positive $x$,
$$1+\frac{1}{\eta-1} < e^{\frac{1}{\eta -1}}\,.$$  Therefore, 
$$\left(1+\frac{1}{\eta-1}\right)^{\alpha-1} < e^{\frac{\alpha-1}{\eta-1}}\le e < \eta-1$$ (since $\alpha\le \eta$). Multiplying both sides by $(\eta-1)^{\alpha-1}$, we obtain
$$\eta^{\alpha-1} < (\eta-1)^\alpha\,.$$
Taking the logarithm of both sides yields the statement of the lemma.
\end{proof}

@@

%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.  We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
\begin{definition}
A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
\end{definition}

@@

\begin{lemma}
$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
\end{lemma}
\begin{proof}
By the isoperimetric inequality on the Hamming space~(we use a version due to~\cite[Theorem 1]{frankl1981short}, the original result is due to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient ball $S_{p^*, \key^*}$ centered at $0$ and a set $D$ such that $|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*, \key^*}^\complement|$ and $\forall s\in S_{p^*, \key^*}, d\in D$, $\dis(s, d) \ge t$~(alternatively, the distance between the sets is $t$).  Furthermore, note that $S_{p^*, \key^*} \cup D$ is a deficient ball~(and its radius is $\eta+t$).
We now find bound the size of $S_{p^*, \key^*}$.
